Summer 2024 Report

### 2024-11-14 Relations/Report.tex
Updates for meeting 14th Nov

@@

\section{Relations}

\subsection{Well-foundedness}
\sacomment{Talk about the different types of wellfoundedness, starting with the one given in the book, the reason for thinking it is classical and not constructive, and provide an image showing the relation between the notions of wellfoundedness we have. Talk about future work in this area.}

@@

\subsection{Definitions}
\textcolor{red}{Go through some of the main definitions formalised from Terese, focussing on where we have used constructive alternatives to the classically given definitions
Could talk here about omega bounded stuff too!}

The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3. Before exploring those proofs the following definitions are essential.

\begin{dfn}
  An abstract reduction system (\emph{ARS}) is a structure $\mathcal{A} = (A, \to_\alpha)$ where $A$ is a set and $\to_\alpha$ is a set of binary relations.
\end{dfn}
A relation $\to$ from the set $\to_\alpha$ is refered to as a reduction (or rewrite) relation. For example, if we specify $\to$ as the relation of being 'less than' ($<$) then $4 \to 2$. \textcolor{red}{Right?}
\apcomment{Yes, but move this to a(n eventual) list of examples.}

We use $\to$ for a single-step reduction and $\tto$ for a multi-step reduction.

\begin{dfn}
    A reduction relation is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if all single-step reductions from a given element can always converge via multi-step reductions to some common reduct.
\end{dfn}
\begin{figure}[h]
  \centering
\[  \begin{tikzpicture}[node distance=1.5cm, auto]
    % Nodes
    \node (top) {a};
    \node (left) [below left of=top] {b};
    \node (right) [below right of=top] {c};
    \node (bottom) [below right of=left] {d};

  % Arrows
  \draw[->>] (top) -- (left);
  \draw[->>] (top) -- (right);
  \draw[->>] (left) -- (bottom);
  \draw[->>] (right) -- (bottom);
\end{tikzpicture}
\]
\caption{An example of a weakly confluent relation.}
\end{figure}

\begin{dfn}
  A reduction relation is \emph{confluent} (AKA Church-Rosser (CR)) if all multi-step reductions from a given element can always converge via multi-step reductions to some common reduct.
\end{dfn}
    \begin{figure}
      \centering
      \begin{tikzpicture}[node distance=1.5cm, auto]
        % Nodes
        \node (top) {a};
        \node (left) [below left of=top] {b};
        \node (right) [below right of=top] {c};
        \node (bottom) [below right of=left] {d};

        % Arrows
        \draw[->>] (top) -- (left);
        \draw[->>] (top) -- (right);
        \draw[->>] (left) -- (bottom);
        \draw[->>] (right) -- (bottom);
      \end{tikzpicture}
    \caption{An example of a confluent relation.}
    \end{figure}

  A relation $\to$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
\end{dfn}
\sacomment{A lot of these are near word for word from TeReSe, is that okay?}

  A relation $\to$ is strongly normalizing (SN) if every
  $a \in A$ is $\to$-strongly normalizing.
\end{dfn}

The above definition of SN is taken from TeReSe. We make use of the alternative definition presented in TeReSe ($\leftarrow$ is accessibly well-founded) when working in Agda.

If $\to$ is a reflexive, transitive and symmetric relation we denote it $\to^=$.

\apcomment{This is not quite right; rather, $\to^=$ is the reflexive-symmetric-transitive closure of $\to$, i.e., it is the \emph{equivalence relation generated by $\to$}, the NFP refers to this latter relation.}

\apcomment{Add a subsection/definition listing the closure operations on relations.}

\begin{dfn}
  A reduction relation $\to$ has the \emph{normal form property} (NFP) if
 $a \to^= b$  $\implies$
 $a \tto b$, for all $a \in A$ and any normal form $b \in A$.
\end{dfn}

$a, b \in A$ being equivalent is denoted $a \equiv b$.

\begin{dfn}
  $\to$ has the \emph{unique normal form property} (UN) if
  $a \to^= b$  $\implies$
  $a \equiv b$, for all $a \in A$ and any normal form $b \in A$.
\end{dfn}

\begin{dfn}
  $\to$ has the \emph{unique normal form property with respect to reduction} (UN$^ \to$) if
  $a \twoheadleftarrow  \cdot  \tto b$  $\implies$ $a \equiv b$, for all normal forms $a,b \in A$.
\end{dfn}

          \draw[->>] (f0) -- (a);
          \draw[->>] (f1) -- (a);
          \draw[->>] (dots) -- (a);
      \end{tikzpicture}
      \caption{An example of an $\omega$-bounded sequence.}

\begin{dfn}
  $a \in A$ has the \emph{recurrence property} if $a \tto b \implies b \tto a$ for all $b \in A$.
\end{dfn}
\sacomment{I've been using $\tto$ as interchangable with $R *$ (as in the above definition).
Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
\apcomment{It's okay, but later we will need to make sure we are using them consistently.  Say that in Agda code, $\to$ is denoted by $R$.}

\begin{dfn}
  $\to$ has the \emph{recurrence property} (RP) if every
  bounded, increasing sequence has a recurrent element.
\end{dfn}

        \end{figure}
\begin{dfn}
  $\to$ has the \emph{weak recurrence property} (RP-) if
  for every increasing sequence with bound $a$,
  there is an element $i$ of the sequence such that $a \tto f (i)$.
\end{dfn}

\begin{dfn}
  $\to$ is \emph{finitely branching} (FB) if, for all $a \in A$, the set of one step reducts of $a$ is finite.
\end{dfn}

\subsection{Newmans lemma}
What it is and the different definitions again

\subsection{}

\section{Notes from 08.29}

@@

\section{09.05}
\begin{enumerate}
  \item done: WN, UN, RP imply SN (classical)
  \item need: omega bounded and RP implies SN (classical)
  \item need: omega bounded and RP implies SN (constructive)
  \item do we need $s_0 \to^* s_c$ in the proof?
  \item is $\omega$-bounded implied by WN and the following confluence property:
  $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
  \item Remark before 1.2? (Exercise 1.3.21)
  \item Make the first argument to "being a normal form" implicit?
\end{enumerate}

>>>>

\tableofcontents

@@

\section{Definitions}
The most interesting work we have carried out in investigating Chapter 1 of TeReSe has resulted from trying to provide constructive proofs for Newman's lemma, the Knaster-Tarski lemma, theorem 1.2.2 and theorem 1.2.3. Before exploring those proofs the following definitions are essential.

\begin{dfn}
  An abstract reduction system (\emph{ARS}) is a structure $\mathcal{A} = (A, R_\alpha)$ where $A$ is a set and $R_\alpha$ is a set of binary relations.
\end{dfn}
A relation $R$ from the set $R_\alpha$ is refered to as a reduction (or rewrite) relation. For example, if we specify $R$ as the relation of being 'less than' ($<$) then $R\, 4\, 2$. \textcolor{red}{Right?}
\apcomment{Yes, but move this to a(n eventual) list of examples.}

We use $R$ or $\to$ for a single-step reduction and $R^*$ or $\tto$ for a multi-step reduction.

\sacomment{Should we be using $R^+$ rather than $R^*$?}

\begin{dfn}
  An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step reductions from $a$ can always converge 
  via multi-step reductions to some common reduct.  
  A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
\end{dfn}

\begin{dfn}
  An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step reductions from $a$ can always converge 
  via multi-step reductions to some common reduct.  
  A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
\end{dfn}

\begin{figure}[h]
  \centering
\[  \begin{tikzpicture}[node distance=1.5cm, auto]
    % Nodes
    \node (top) {a};
    \node (left) [below left of=top] {b};
    \node (right) [below right of=top] {c};
    \node (bottom) [below right of=left] {d};

  % Arrows
  \draw[->>] (top) -- (left);
  \draw[->>] (top) -- (right);
  \draw[->>] (left) -- (bottom);
  \draw[->>] (right) -- (bottom);
\end{tikzpicture}
\] 
\caption{On the left is an example of a weakly confluent relation. On the right is an example of a confluent relation.}
\end{figure}

  A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
\end{dfn}

  A relation $R$ is strongly normalizing (SN) if every
  $a \in A$ is $R$-strongly normalizing.
\end{dfn}

The above definition of SN is taken from [TeReSe]. When working in Agda, we make use of the alternative definition presented in [TeReSe] ($\leftarrow$ is accessibly well-founded).

\subsection{Closure operations on relations}

A relation $R$ has the following properties when the stated conditions are met:
\begin{dfn}
  \emph{reflexive} {- $\forall x \in A : x \to x $}    
\end{dfn}
\begin{dfn}
  \emph{transitive} {- $\forall x, y, z \in A : ( x \to y \land y \to z ) \implies x \to z $}    
\end{dfn}
\begin{dfn}
  \emph{symmetric} {- $\forall x, y \in A : x \to y \implies y \to x$}    
\end{dfn}

\begin{dfn}
  The \emph{closure} of $R$ is the smallest relation that contains $\to$ and satisfies a given property. 
\end{dfn}

\begin{dfn}
  The \emph{reflexive closure} of $R$ is the smallest relation $\to^r$ that contains $\to$ and is reflexive.
\end{dfn}
\begin{dfn}
  The \emph{symmetric closure} of $R$ is the smallest relation $R^s$ that contains $R$ and is symmetric.
\end{dfn}
\begin{dfn}
  The \emph{transitive closure} of $R$ is the smallest relation $R^+$ that contains $R$ and is transitive. 
\end{dfn}
\begin{dfn}
  The \emph{reflexive transitive closure} of $R$ is the smallest relation $R^*$ that contains $R$ and is both reflexive and transitive. 
\end{dfn}
\begin{dfn}
  The \emph{equivalence relation} of $R$ is the smallest relation $R^=$ that contains $R$ and is reflexive, transitive, and symmetric.
\end{dfn}

\begin{dfn}
  A relation $R$ has the \emph{normal form property} (NFP) if
 $a \to^= b$  $\implies$
 $a \tto b$, for all $a \in A$ and any normal form $b \in A$.
\end{dfn}

Two elements $a, b \in A$ being equivalent is denoted $a \equiv b$.

\begin{dfn}
  A relation $R$ has the \emph{unique normal form property} (UN) if
  $a \to^= b$  $\implies$
  $a \equiv b$, for all $a \in A$ and any normal form $b \in A$.
\end{dfn}

\begin{dfn}
  A relation $R$ has the \emph{unique normal form property with respect to reduction} (UN$^ \to$) if
  $a \twoheadleftarrow  \cdot  \tto b$  $\implies$ $a \equiv b$, for all normal forms $a,b \in A$.
\end{dfn}

          \draw[->>] (f0) -- (a);
          \draw[->>] (f1) -- (a);
          \draw[->>] (dots) -- (a);
      \end{tikzpicture}
      \caption{An example of an bounded sequence.}

\begin{dfn}
  An element $a \in A$ has the \emph{recurrence property} if $a \tto b \implies b \tto a$ for all $b \in A$.
\end{dfn}
\sacomment{I've been using $\tto$ as interchangable with $R *$ (as in the above definition).
Is that okay or am I going to have to clarify why they are interchangable (are they not interchangable?)?}
\apcomment{It's okay, but later we will need to make sure we are using them consistently.  Say that in Agda code, $\to$ is denoted by $R$.}

\begin{dfn}
  A relation $R$ has the \emph{recurrence property} (RP) if every
  bounded, increasing sequence has a recurrent element.
\end{dfn}

        \end{figure}
\begin{dfn}
  A relation $R$ has the \emph{weak recurrence property} (RP-) if
  for every increasing sequence with bound $a$,
  there is an element $i$ of the sequence such that $a \tto f (i)$.
\end{dfn}

\begin{dfn}
  A relation $R$ is \emph{finitely branching} (FB) if, for all $a \in A$, the set of one step reducts of $a$ is finite.
\end{dfn}

\section{Implications}
We now look into the interrelation of the various properties defined in Section 2. Our aim is to expand on the 
connections made in Figure 1.8 of [TeReSe] (p.19).

\section{Counterexamples}
The following counterexamples are used to rule out certain implications between properties from holding. 
\sacomment{How should we present this section. Is it enough to have diagrams and a list of what they are a counter to?}
\subsection*{Counterexample 1}
\begin{center}

  \begin{tikzcd}[node distance=2cm, auto]
      % Nodes
      \node (a) {a};
      \node (b) [right of=a, xshift=1cm] {b};
      \node (c) [right of=b, xshift=1cm] {c};
      \node (d) [right of=c, xshift=1cm] {d};

      % Arrows
      \draw[->] (b) to [bend left] (c);
      \draw[->] (c) to [bend left] (b);
      \draw[->] (b) -- (a);
      \draw[->] (c) -- (d);
  \end{tikzcd}

\end{center}
Counterexample to:
\begin{itemize}
  \item WCR $\implies$ CR
  \item WCR and WN $\implies$ CR
  \item WCR and WN $\implies$ SN
  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP)}
\end{itemize}
\subsection*{Counterexample 2}
\begin{center}
  \begin{tikzcd}
      % Nodes
      \node (x) {x};
      \node (n) [left of=x, xshift=-1cm] {n \in NF};
      \node (y) [right of=x, xshift=1cm] {y};
      \node (z) [right of=y] {z};

      % Arrows
      \draw[->>] (x) -- (n);
      \draw[->>] (x) -- (y);
      \draw[->] (y) to [bend left] (z);
      \draw[->] (z) to [bend left] (y);
  \end{tikzcd}
\end{center}

Counterexample to:
\begin{itemize}
  \item WN$\downarrow\subseteq$WN (WN is not closed under reduction) \sacomment{Is this the right way to express that elementwise WN doesn't imply global WN?}
  \item WN$\downarrow$UN$\rightarrow\subseteq$WN :

  UN$\rightarrow\,$R $\to \forall$ x $\to$ is R-WN x $\to$ $\forall$ y $\to$ (R *) x y $\to$ is R-WN y

  \textcolor{red}{SA: The above is a bit messy, can we make it cleaner?}
  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$

\end{itemize}

\subsection*{Counterexample 3}

\begin{center}
  \begin{tikzcd}
      % Nodes
      \node (x) {x};

      % Arrows
      \draw[->, loop] (x) to (x);
  \end{tikzcd}
\end{center}
Counterexample to:
\begin{itemize}
  \item bounded and RP implies SN
  \item bounded and RP implies WN
\end{itemize}

\subsection*{Counterexample 4}
  \begin{center}
      \begin{tikzpicture}
      % Define the nodes 
      \node (a) at (0, 0) {$a$};
      \node (b) at (1, 0) {$b$};
      \node (dots) at (2, 0) {$...$};

      % Draw the arrows
      \draw[->] (a) -- (b);
      \draw[->] (b) -- (dots);

      \end{tikzpicture}
    \end{center}
Counterexample to:

\section{Well-foundedness}
\subsection{Well-foundedness}
\sacomment{Talk about the different types of wellfoundedness, starting with the one given in the book, the reason for thinking it is classical and not constructive, and provide an image showing the relation between the notions of wellfoundedness we have. Talk about future work in this area.}

@@

\section{Notes}
\subsection{Notes from 08.29}

@@

\subsection{09.05}
\begin{enumerate}
  \item done: WN, UN, RP imply SN (classical)
  \item need: omega bounded and RP implies SN (classical)
  \item need: omega bounded and RP implies SN (constructive)
  \item do we need $s_0 \to^* s_c$ in the proof?
  \item is $\omega$-bounded implied by WN and the following confluence property:
  $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
  \item Remark before 1.2? (Exercise 1.3.21)
  \item Make the first argument to "being a normal form" implicit?
\end{enumerate}

### 2024-11-14 Relations/notes.tex
Updates for meeting 14th Nov

\textbf{Primary Goal: A technical report that focuses on
Abstract Rewriting in Constructive Setting }

\section{2024.10.31}

Rewriting properties.
Elementwise
\begin{itemize}
  \item NF
  \item WN
  \item SN
  \item WCR
  \item CR
  \item NFP
  \item UN$\to$
  \item UN
  \item RP
  \item RP$-$
  \item $\omega$-bound
  \item Recurrent
  \item CP (Cofinality property)
  \item FB (Finite branching of rewrite steps)
  \item DominatedByWF (Needed?)
  \item Define WNFP to be:
  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
  \item Does WNFP and WN imply CR?  Looks like it!
  \item Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)

  Could even consider $SN^*$, $CR^*$ etc.
\end{itemize}
Most of these properties $P$ have a ``global'' version $P^\forall$, asserting that $\forall x. P(x)$ holds.

Other properties that show up in classical ARS theory:
\begin{itemize}
  \item Inc
  \item Ind
  \item $\mathrm{CR}^{\le 1}$
\end{itemize}
Want to discuss these, and why we may or may not include them in our
development.

Outline of the document:
\begin{enumerate}
  \item Create a diagram with implications between these, and
  combinations of these, similar to the one in TeReSe.
  \item Formalization of valid implications
  \item Counterexamples: Compile a list/chart/graph of those relationships
  which can be disproved. (A big part!!)
  \item A list of classical properties, and elaboration of their meaning
  and whether it's reasonable to assume them in a rewriting context.
  (Discuss each, and its role in ARS theory.)
  \item Well-foundedness: different constructive formulations, and relationships between them
  \item ``Guide'' to the formalization code, GitHub repo
  \item Discussion of open problems (Add a subsection of these at the end of each section?)
  \item Conclusion
\end{enumerate}

\section{Established implications:}

\begin{itemize}
  \item SN implies $\omega$-bounded
\end{itemize}

\section{2024.10.10}

\begin{itemize}
  \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
  \item Status of important hypotheses:
    \begin{itemize}
      \item Deciding whether a given element $x$ reduces to a given element $y$
      (Is $R$ itself decidable?)
      \item Deciding whether a given element $x$ reduces to some element $y$
      (Is being an $R$-normal form decidable?)

@@

      \item Does UN-lemma \emph{require} the decidability assumption?
    \end{itemize}
  \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
  for example,
  \begin{itemize}
    \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
    \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
  \end{itemize}
  \item When time permits, uniformize the notation (variable names, etc.) to the extent possible.
\end{itemize}

\section{2024.09.19}

TODO item: Compile a list of counterexamples

\section{2024.09.12}
\begin{itemize}
  \item Investigate \texttt{iii-lemma}.  (Is it false, or is there a classical proof?)
  (No constructive proof?)
  \item Look at variations of RP.
  \item What happens if properties involving sequences are reformulated for
  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
  \item Look at RP- and WCR implies RP!
  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
  be related to the cofinality property.
\end{itemize}

\section{Relations, ARS}

\begin{enumerate}
  \item Define logical and structurual operations on relations, proving laws about them.
  \item Define closure operations on realtions, proving laws about them
  \item Define properties such as transtivity etc.
\end{enumerate}

\subsection{Well-foundedness}

Four notions:
\begin{itemize}
  \item Based on every element being accessible
  \item Every inductive relation is universally true
  \item Every non-empty set has a minimal element
  \item No infinite sequence is decreasing
\end{itemize}

\section{Open research questions}
\begin{enumerate}
  \item Sufficient conditions for reversing the implications between notions of
  well-foundedness?
  \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
  \item Syntax for closure operators allowing to prove the needed properties
  uniformly/generically
\end{enumerate}

\section{To Do}
\begin{enumerate}
  \item Clean up the current development
  \item More laws about closure operations: Monotonicity, idempotency
  \item Refactor the ARS formalized results with the new development
  \item Knaster--Tarski in a well-founded setting: what additional
  hypotheses are necessary?
\end{enumerate}

\subsection{Questions about well-foundedness}

\begin{enumerate}
  \item For a given element $x$, is the property of
  being accessible $\lnot\lnot$-closed? I.E.,
  Does $x$ being $\lnot\lnot$-accessible imply that $x$ is accessible?
  (Conjecture: No.)

@@

   \emph{Note.}  This seems to require the most classical assumptions:
   $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
   Markov's principle, etc.

   \item (2024.10.10) Is being $R$-WN inductive?
   \item (2024.10.10) Does $R$ being finitely branching imply
   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
   $\exists y. Rxy \land \lnot \phi(y)$?

@@

\textsc{Remark.}
$\lnot\lnot$-closure of accessibility should solve problems 1 and 4.

\section{Open problems}

\begin{itemize}
  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.

  So, does $WN, RP, WCR$ imply $\omega$-bounded?
  Answer: yes, that is what we have proved classically.

  \item Wait, does RP- actually imply RP????

  \item RP- and $\omega$-bounded implies RP?
  \item RP- and WCR imply RP?
  \item
  \[ WNg \land UN \to CRelem :
  \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
  \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
\end{itemize}

>>>>

This document aims to bring together the various notes from report, rewriting qs, and counterexamples.

\section{Todo}
\subsection*{Week starting 11th November}
\begin{enumerate}
  \item In the report, give a classical proof that the $Inc$ Property
  implies that no $R$-increasing sequence is bounded.

  Conclude that every relation satisfying $Inc$ also satisfies $RP$.

  Therefore, the proof of Theorem 1.2.3(iii) using $RP$ instead of $Inc$
  is generalizing the claim of the theorem (as stated in [TeReSe]).
  \item Complete the proof in ARS.agda of Theorem 1.2.3.(iii)
  \item Organize notes.tex into three sections: TODO, Open Qs, What we've proved. Make sure all notes from the other
  tex files are sorted here correctly.
  \item Tidy up and standardize the notation used in ars.agda and other agda files 
  \item Carry on working through report.tex.  
  \item 
\end{enumerate}
\subsection*{General todo}
\begin{enumerate}

  \item  Make the first argument to "being a normal form" implicit?
  \item Define WNFP to be:
  \[\forall a b c \to b \in NF \to a R^* b \to a R^* c \to c R^* b \]
  \item Does WNFP and WN imply CR?  Looks like it!
  \item  Another interesting one? $WN^*$: hereditarily $WN$ ($WN$ for the reduction graph starting from a given element $x$.)

  Could even consider $SN^*$, $CR^*$ etc.
  \item Define: Inc
  \item Define: Ind
  \item Define: $\mathrm{CR}^{\le 1}$
  \item capture all classical properties/asssumptions we might want to use and justify their use. 
  \item Principles we are considering
  \begin{itemize}
    \item Decidability of equality on $A$
    \item Decidability of the relation $R$
    \item When relevant, decidability of the given precicate $P$
    \item Not-not-closure of being accessible
    \item Not-not-closure of $R$
    \item Not-not-closure of $P$
    \item Decidability of whether a given element is an $R$-normal form
    \item When relevant, local/element-wise versions of the above
    \item Markov's principle:
    \begin{itemize}
      \item In $wfMin_0 \to wfSeq$.

      Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.

      Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
      \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
            \to \big(\exists n \in \nat. s n \equiv a\big)\]

    \end{itemize}
  \end{itemize}
  \item Write a guide to the code
  \item More laws about closure operations: Monotonicity, idempotency

\end{enumerate}
\newpage
\section{Open Questions }
\begin{enumerate}
  \item
     \[ WNg \land UN \to CRelem :
     \forall (R : \mathscr{R} A) \to WN R \to \forall x \to is R -UN x \to is R -CR x \]
     \item $WN R \to UN R \to \omega-bdd R \to SN R$ (1.2.3.ii-)
      \item Finish formulating the ``compactness property".  Two candidates:
       \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
       \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
       \item is $\omega$-bounded implied by WN and the following confluence property:
       $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
  \item (2024.10.10) Is being $R$-WN inductive?
  \item (2024.10.10) Does $R$ being finitely branching imply
   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
   $\exists y. Rxy \land \lnot \phi(y)$?

  \item If WCR holds, is WN$\downarrow\subseteq$WN ?
  \item Same question for next bullet in 2.2
  \item Same for bullet 3 in 2.2 (but pointwise!)
  \item \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
  \item Status of important hypotheses:
    \begin{itemize}
      \item Deciding whether a given element $x$ reduces to a given element $y$
      (Is $R$ itself decidable?)
      \item Deciding whether a given element $x$ reduces to some element $y$
      (Is being an $R$-normal form decidable?)

@@

      \item Does UN-lemma \emph{require} the decidability assumption?
    \end{itemize}
  \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
  for example,
  \begin{itemize}
    \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
    \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
  \end{itemize}
  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
    be related to the cofinality property.
    \item What happens if properties involving sequences are reformulated for
  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
  \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
  \item Knaster--Tarski in a well-founded setting: what additional
  hypotheses are necessary?
\end{enumerate}
\subsection*{well-foundedness}
\begin{enumerate}
  \item For a given element $x$, is the property of
  being accessible $\lnot\lnot$-closed? I.E.,
  Does $x$ being $\lnot\lnot$-accessible imply that $x$ is accessible?
  (Conjecture: No.)

@@

   \emph{Note.}  This seems to require the most classical assumptions:
   $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
   Markov's principle, etc.
   \textsc{Remark.}
   $\lnot\lnot$-closure of accessibility should solve problems 1 and 4.

@@

\newpage 
\section{What has been proven}
\begin{itemize}
  \item \sacomment{List all the constructive proofs we've put together!}
  \item SN implies bounded
  \item RP- implies RP
  \item The infinite haircomb refutes $WN \land RP \to \omega$-bounded.  But it is not WCR.
  \item We have formalized proposition 1.1.9, 1.1.10, 1.1.11 from [TeReSe]. 
  \item We have a proof for Theorem 1.2.1 (Newlman's Lemma) (though we have just one proof of multiple possible proofs).
  \item We have a proof for all parts of Theorem 1.2.2
  \item We have a proof for Theorem 1.2.3 i, iv. 
  \item Reduction closure properties for SN, NF, UN, recurrent property.

  So, does $WN, RP, WCR$ imply $\omega$-bounded?
  Answer: yes, that is what we have proved classically.
\end{itemize}

\newpage
